lord vorotron: finding the best JFA variant for the coming winter

### 2020-09-15 paper/main.tex
more and more
section order

%%% BONUS %%%
\usepackage[table]{xcolor}  % for colors (like `red`)
\usepackage[normalem]{ulem} % for underline
\usepackage{booktabs}       % for better table
\usepackage{bm}             % for special table cell (`cellcolor`)
\usepackage{hhline,soul}    % for `hl` command (highlight text)
\usepackage{amsmath}        % for multi-line math
%%%%%%%%%%%%%

@@

\newcommand{\ourjfa}{Lord Vorotron} % okJFAuto / JFAstar
%\title{A survey of \emph{jump flooding algorithm} applied to Voronoi}
% \emph{\ourjfa}: Evolving Fast GPU Algorithm for
% Voronoi Diagram and Distance Transform in O(1) from JFA using AutoML
\title{lord vorotron: finding the best JFA variant for the coming winter} % $\approx$

@@

@@

This paper studies a practical usage of machine learning to automate research
towards discovering efficient Distance Transform algorithms (utilizing technique known as AutoML).
Thus, by finding mutations which works best for specific data, and then ensembling them into
one, we create new state-of-the-art algorithm in this field named \uline{\ourjfa \hspace{0.01cm} with
time complexity $\approx$O(1) and work complexity $\approx$O(N).}

@@

\begin{enumerate}
\item Presenting new state-of-the-art version of JFA made as envolved ensemble of weak learners; and
\item Proposing, for an input set of seeds in a 2D grid, the first
parallel algorithm in GPU to compute in constant time (i.e.
independent of the number of seeds) a highly accurate
Voronoi diagram and distance transform.
\end{enumerate}

@@

@@

\hl{bridge z score function gdziekolwiek to bedzie}

jakie modyfikacje, na to osobna sekcja? wiec co tu napisac

@@

\hl{ZROBIC LADNE RYSUNECZKI w Google Slides - eksport to pdf!}
wyjasnic slownictwo? np. co okreslamy przez anchor

>>>>

%%% BONUS %%%
\usepackage[table]{xcolor}  % for colors (like `red`)
\usepackage[normalem]{ulem} % for underline
\usepackage{booktabs}       % for better table
\usepackage{bm}             % for special table cell (`cellcolor`)
\usepackage{hhline,soul}    % for `hl` command (highlight text)
\usepackage{amsmath}        % for multi-line math
\usepackage[bottom]{footmisc}% for footnotes
%%%%%%%%%%%%%

@@

\newcommand{\ourjfasingle}{JFAStar}
\newcommand{\ourjfa}{Lord Vorotron} % okJFAuto / JFAstar
%\title{A survey of \emph{jump flooding algorithm} applied to Voronoi}
% \emph{\ourjfa}: Evolving Fast GPU Algorithm for
% Voronoi Diagram and Distance Transform in O(1) from JFA using AutoML
\title{lord vorotron: finding the best JFA variant for the coming winter} % $\approx$

@@

\hl{\textbf{CEL:} omawiamy dwa algorytmy? jeden nastepca JFA} -
\textbf{\ourjfasingle} \hspace{0.01cm} \hl{oraz ensembla po naszym score fn. -}
\textbf{\ourjfa}???????

@@

% FIXME: na wypadek zmiany tytulu w przyszlsoci!!!!!!!!!! ;-)
This paper\footnote{the original title for this paper was ``Lord Vorotron:
Finding the Best JFA Variant for the Coming Winter''} studies a practical usage of machine learning to automate research
towards discovering efficient Distance Transform algorithms (utilizing technique known as AutoML).
Thus, by finding mutations which works best for specific data, and then ensembling them into
one, we create new state-of-the-art algorithm in this field named \uline{\ourjfa \hspace{0.01cm} with
time complexity $\approx$O(1) and work complexity $\approx$O(N).}

@@

\begin{enumerate}
	\item Presenting new state-of-the-art variants of algorithm for Voronoi
		Diagram and Distance Transform: \newline
		\textbf{\ourjfasingle} - single best variant;
		\textbf{\ourjfa} - ensemble of weak variants; and
	\item Analyzing all possible variants of JFA: comparing error and speedup
		relative to bruteforce method
%\item Proposing, for an input set of seeds in a 2D grid, the first
%parallel algorithm in GPU to compute in constant time (i.e.
%independent of the number of seeds) a highly accurate
%Voronoi diagram and distance transform.
\end{enumerate}

@@

okay przenioslem - dodac prace co tez tak szuka algosow

@@

\hl{bridge z score function gdziekolwiek to bedzie}
\hl{obliczyc ile jest aktulanie wersji algosow np. czy jest to juz 2do14 jak
mamy 3xreal w wielomianie}

jakie modyfikacje, na to osobna sekcja? wiec co tu napisac
chyba tylko o zlozonosci problemu i ze kod jest skladany i testowany a niektore
wersje sa pomijane zgodnie z dzialaniem gp\_minimize (Bayesian optimization
using Gaussian Processes).

\subsection{Score Function} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hl{SCORE CZY METRIC?}
\hl{roznica w pikselach pomiedzy bruteforce a algorytmem - napisac o tym / tez
ze to wszystko to ilorazy do bruteforce}

@@

\hl{ZROBIC LADNE RYSUNECZKI w Google Slides - eksport to pdf!}
wyjasnic slownictwo? np. co okreslamy przez anchor
i wyjasnic jak powstaly nazwy? np. Circle11Dual|Factor3+Noise
